### 2020-10-08 README.Rmd

plot(resampling, task, crs = 4326)
```

### Visualization of a specific fold

```{r spcv_coords-fold}
plot(resampling, task, fold_id = 1, crs = 4326)
```

>>>>

autoplot(resampling, task, crs = 4326) +
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) +
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

### Visualization of specific folds

```{r spcv_coords-fold}
autoplot(resampling, task, fold_id = c(1, 2), crs = 4326) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```
